---
title: "ADC-US-RES-22225 `r params$title2`"
author: "Alvin, Lin"
date: "`r Sys.Date()`"
format:
   html:
     theme: flatly
     self-contained: true
toc: true
toc-depth: 3
toc-location: left
execute:
  echo: false
  warning: false 
  keep-md: true
column: body-outset
params:
    upload: FALSE
    plot: TRUE
    type : "904"
    analysis: FALSE
    title1: "Upload Quality"
    title2: "Profile Plot"
    title3: "Accuracy Performance"
---

<!-- AUU \\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\UploadData\AUU\AUU_Datafiles -->

<!-- EDC \\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\OpenClinica\Current -->

```{r}
#| label: Libaray Packages 
#| message: false
library(magrittr)
library(plyr)
library(tidyverse)
library(fs)
library(vroom)
library(lubridate)
library(htmltools)
library(reactable)
library(highcharter)
library(haven)
library(gt)
library(arrow)
```

```{r}
#| label: Find all events and gluc files csv
file_list <- dir_ls(gsub("\\\\", "/", r"(\\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\UploadData\AUU\AUU_Datafiles)"),recurse = T,glob = "*events.csv|*gluc.csv|*freestyle.csv")
```

```{r}
#| label: Filter all and find events 
events_path <- file_list[!str_detect(file_list,"Transfers|FV_Do Not Use") & str_detect(file_list,"events")]
```

```{r}
#| label: Filter all and find gluc
gluc_path <- file_list[!str_detect(file_list,"Transfers|FV_Do Not Use") & str_detect(file_list,"gluc")]
```

```{r}
#| label: Filter freestyle
free_path <- file_list[!str_detect(file_list,"Transfers|FV_Do Not Use") & str_detect(file_list,"freestyle")]
```

```{r}
# de <- read_sas(gsub("\\\\", "/", r"(\\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\OpenClinica\Current\de.sas7bdat)")) %>%  
#   filter(!str_detect(DEYN01,regex("CHECK HERE IF NO DATA RECORDED|no_data_recorded",ignore_case = T))) %>%
#   mutate(Subject = as.character(Subject)) %>%
#   arrange(Subject)
```

```{r}
# pd <- read_sas(gsub("\\\\", "/", r"(\\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\OpenClinica\Current\pd.sas7bdat)")) %>%   
#   filter(!str_detect(DVYN,regex("CHECK HERE IF NO DATA RECORDED|no_data_recorded",ignore_case = T))) %>%
#   mutate(Subject = as.character(Subject)) %>%
#   arrange(Subject)
```

```{r eval = params$upload}
Upload_fun <- function(upload,n,count,...){
  ## Counts
  if (count == T){
    tibble(`Subject ID` = str_extract(events_path,regex("(?<=Apol0).{6}|(?<=Atna0).{6}",ignore_case = T)),
           `Condition ID` = str_extract(events_path,regex("(?<=_{7}).{3}",ignore_case = T)),
           Path = gsub("/","\\\\",str_remove(events_path,regex("(?<=/[:digit:]{9}).++")))) %>% 
           count(`Subject ID`,Path,name = "N") %>% 
           # Add parameters
           filter(N != n) %>%
   reactable(defaultColDef = colDef(align = "center"), wrap = TRUE, striped = TRUE, resizable = TRUE,
    columns = list(Path = colDef(cell = function(value) {
      htmltools::tags$a(href = value, target = "_blank", value)
    }
      )
    )
  )
  } else {
     ## Empty
  data <- vector("list",length(upload))
for (i in 1:length(upload)) {
   data[[i]] <- vroom(upload[i],delim = ",",col_names = T,show_col_types = F,col_select = `Unique Record ID`)  
}
  
  tibble(Path = gsub("/","\\\\",upload[map_dbl(data,nrow) == 2])) %>%
       mutate(`Subject ID` = str_extract(Path,regex("(?<=Apol0).{6}||(?<=Atna0).{6}",ignore_case = T)),
              `Condition ID` = str_extract(Path,regex("(?<=_{7}).{3}",ignore_case = T)),
              `Reader Serial Number` = map_chr(data[map_dbl(data,nrow) == 2], ~ str_extract(.x[2,1],regex("(?<=\\s).{13}",ignore_case = T)))) %>%
       left_join(de %>%
                 select(Subject,DESPID01,DETXT02,DEORES02) %>%
                 mutate(DESPID01 = str_to_upper(DESPID01),
                 DETXT02 = str_replace_all(DETXT02,"\"","")) %>%
                 group_by(Subject,DESPID01) %>%
                 summarise_all(funs(str_c(., collapse = ". "))) %>% 
                 mutate(`Message from DIR` = str_c(DETXT02,DEORES02,sep = ". "),
                `Message from DIR` = str_to_sentence(
                 case_when(
                str_starts(`Message from DIR`,"\\.") ~ str_extract(`Message from DIR`,"(?<=[:space:])[:alpha:].+"),
            TRUE ~ `Message from DIR`
          )),
          DEORES02 = NULL,
          DETXT02 = NULL
                       ),by = c("Subject ID" = "Subject","Reader Serial Number" = "DESPID01")) %>%
       left_join(pd %>% 
                 select(Subject,DVDESC1) %>% 
                 group_by(Subject) %>% 
                 summarise_all(funs(str_c(., collapse = ' '))) %>%
                 mutate(`Message from PD` = str_to_sentence(DVDESC1),
                        DVDESC1 = NULL),
                 by = c("Subject ID" = "Subject")
                 ) %>%  
       relocate(`Subject ID`,`Condition ID`) %>%  
  reactable(defaultColDef = colDef(align = "center"), wrap = TRUE, striped = TRUE, resizable = TRUE,
    columns = list(Path = colDef(cell = function(value) {
      htmltools::tags$a(href = value, target = "_blank", value)
    }
      )
    )
  )
  }
}
```

`r if(params$upload){knitr::asis_output("# **Count of Upload**")}`
```{r eval = params$upload}
#| warning: false
#| column: page
Upload_fun(upload = events_path,n = 4,count = T)
```

```{r eval = params$upload}
knitr::knit_exit()
```

```{r}
#| label: Apol function
#| warning: false
Apol_fun <- function(index, ...){
    # Read Events csv
    events <- vroom(events_path[index],delim = ",",col_names = T,show_col_types = F,col_types = c(`Col 9` = "c"),col_select = c(Date,Time,Type,`Col 9`))
    # Read Gluc csv
    gluc <- vroom(gluc_path[index],delim = ",",col_names = T,show_col_types = F,col_types = c(Type = "c"),col_select = c(`Unique Record ID`,Date,Time,Type,Gl))
    
    if (nrow(events) == 2 && nrow(gluc) == 2) {tibble()}
    else {
          # Time is NA with vroom function
          if (sum(is.na(gluc$Time)) > 2) {
          gluc <- vroom(gluc_path[index],delim = ",",col_names = T,show_col_types = F,col_types = c(Type = "c"),col_select = c(`Unique Record ID`,Date,Time,Type,Gl),n_max = 2) %>%
   bind_rows(data.table::fread(gluc_path[index],skip = 2,select = c(1:5),col.names = c("Unique Record ID","Date","Time","Type","Gl"),colClasses = c("V2" = "Date","V4" = "character")))
          }
      
          events <- events %>%
                    filter(Type == "SENSOR_STARTED (58)") %>%
                    transmute(
                            `Date Time` = ymd_hms(str_c(ymd(Date),hms::as_hms(Time),sep = " ")),
                             Type = Type,
                            `Sensor Serial Number` = `Col 9`
                              ) %>%
                # Consider Replaced Sensors
                slice_max(`Date Time`,n = 1)
          
          ## Extract Subject ID, Condition ID, Reader ID.
      gluc <- gluc %>%
              transmute(`Subject ID` = case_when(
              str_extract(gluc[1,1],regex("(?<=Site ID = ).{3}",ignore_case = T)) == "ADC" ~ str_extract(gluc[1,1],regex("(?<=Subject ID = ).{4}",ignore_case = T)),
                        TRUE ~ str_c(str_extract(gluc[1,1],regex("(?<=Site ID = 0).{2}",ignore_case = T)),str_extract(gluc[1,1],regex("(?<=Subject ID = ).{4}",ignore_case = T)))),
                   `Condition ID` = str_extract(gluc[1,1],regex("(?<=Condition ID = ).{3}",ignore_case = T)),
                  `Reader ID` = str_extract(gluc[2,1],regex("(?<=\\s).{13}",ignore_case = T)),
                  `Date Time` = ymd_hms(str_c(ymd(Date),hms::as_hms(Time),sep = " ")),
                         Type = Type,
                           Gl = Gl) %>%
                   slice(3:n())
          ## Bind rows Events with Gluc
          events %>%
            bind_rows(gluc) %>%
            fill(c(`Subject ID`,`Condition ID`,`Reader ID`),.direction = "up") %>%
            fill(`Sensor Serial Number`,.direction = "down") %>%
            relocate(`Subject ID`,`Condition ID`,`Sensor Serial Number`,
                     `Reader ID`,`Date Time`,Type,Gl)
  }
}
```

```{r}
#| label: For Loop UUU
#| warning: false
UUU <- vector("list",length(events_path))
for (i in seq_along(events_path)) {
  UUU[[i]] <- Apol_fun(index = i)
}
```

```{r}
#| label: empty gluc.csv
# tibble(Path = gsub("/","\\\\",gluc_path[which(map_dbl(UUU,nrow) == 1)])) %>% 
#      reactable(defaultColDef = colDef(align = "center"), wrap = TRUE, striped = TRUE, resizable = TRUE,
#     columns = list(Path = colDef(cell = function(value) {
#       htmltools::tags$a(href = value, target = "_blank", value)
#     }
#       )
#     )  )
```

```{r}
#| label: List Rbind UUU
UUU <- UUU %>% 
       list_rbind() %>% 
       # Remove Duplicated Uploads
       distinct()
```

<!-- Delete Code -->

```{r}
# sa <- read_sas(gsub("\\\\", "/", r"(\\wf00168p.oneabbott.com\data1\CDM\ADC-US-RES-22225\SE07_08_Glu\OpenClinica\Current\sa.sas7bdat)"))
```

```{r}
# sa <- sa %>% 
#       filter(!str_detect(DUYN01,regex("CHECK HERE IF NO DATA RECORDED",ignore_case = T))) %>%
#       select(Subject,DUSEQ01,DUCOD01,DUORES06) %>% 
#       mutate(Subject = as.character(Subject)) %>%
#       arrange(Subject) 
```

```{r}
# UUU %>% 
#     distinct(across(`Subject ID`:`Sensor Serial Number`)) %>%
#     full_join(sa,by = c("Subject ID" = "Subject", "Condition ID" = "DUCOD01")) %>% 
#     mutate(`Study Event` = case_when(str_starts(`Subject ID`,"57") ~ "225 SE07",
#                                      TRUE ~ "225 SE08")) %>% 
#     relocate(`Study Event`) %>%
#     rename(`Sensor Number` = DUSEQ01, `Was the sensor functional?` = DUORES06) %>% 
#     arrange(`Subject ID`) %>% 
#     vroom_write(gsub("\\\\", "/", r"(C:\Project\ADC-US-RES-22225\Data.csv)"),delim = ",")
```
<!-- Delete Code -->

```{r}
#| label: Import BG Data
#| warning: false
freestyle <- map(free_path,vroom,delim = ",",col_names = T,show_col_types = F,col_select = c(`Unique Record ID`,Date,Time,`FreeStyle Reading`,Status)) %>% 
   map(
 ~ transmute(.x,`Subject ID` = case_when(
              str_extract(.[1,1],regex("(?<=Site ID = ).{3}",ignore_case = T)) == "ADC" ~ str_extract(.[1,1],regex("(?<=Subject ID = ).{4}",ignore_case = T)),
              ## Remedy For Site ID == 00
              str_extract(.[1,1],regex("(?<=Site ID = ).{2}",ignore_case = T)) == "00" ~ 
                str_c(str_extract(.[1,1],regex("(?<=Site ID = 00).{1}",ignore_case = T)),str_extract(.[1,1],regex("(?<=Subject ID = ).{4}",ignore_case = T))),
                        .default = str_c(str_extract(.[1,1],regex("(?<=Site ID = 0).{2}",ignore_case = T)),str_extract(.[1,1],regex("(?<=Subject ID = ).{4}",ignore_case = T)))
              ),
             `BG Date Time` = ymd_hms(str_c(ymd(Date),hms::as_hms(Time),sep = " ")),
             `FreeStyle Reading` = `FreeStyle Reading`,
              Status = Status
          )) %>% 
   map(~ filter(.x,!is.na(`BG Date Time`))) %>% 
   list_rbind() %>%  
   # Filter Status == 0
   filter(Status == 0) %>% 
   # Calculate Average freeStyle reading if time stamp are same.
   mutate(`FreeStyle Reading` = mean(`FreeStyle Reading`),
          .by = c(`Subject ID`,`BG Date Time`)) %>% 
   # Remove Duplicated 
   distinct() %>% 
   # select Useful Columns
   select(-Status) %>% 
   arrange(`Subject ID`,`BG Date Time`)
```

`r if(params$plot){knitr::asis_output("# **Summary Table**")}`
```{r eval = params$plot}
#| label: Summary Table
UUU %>% 
    group_by(`Site ID` = str_c("0",str_sub(`Subject ID`,1,2))) %>% 
    summarise(`Number of Subject` = n_distinct(`Subject ID`),
              `Number of Sensors` = n_distinct(`Subject ID`,`Condition ID`)) %>% 
    gt() %>%
    cols_align(align = "center")
```

```{r eval = params$plot}
#| label: Profile plot function
my_plot <- function(Id, type, ...) {
  highchart() %>%
  # Add title
  {if (type == "904") hc_title(.,text = str_c("Subject = ",Id, " Real-Time Glucose")) 
   else if (type == "905") hc_title(.,text = str_c("Subject = ",Id, " Historic Glucose")) 
   else hc_title(.,text = str_c("Subject = ",Id, " Current Glucose"))} %>% 
  # hc_title(text = str_c("Subject = ",Id)) %>% 
  # continuous Sensor Data
  hc_add_series(
    # name = "Sensor Reading",
    data = UUU %>%
           filter(`Subject ID` == Id, Type == type) %>% 
           # 904 is Real-time glucose 906 is current glucose
           mutate(Type = case_when(Type == "906" ~ "Current Glucose",
                                   Type == "904" ~ "Real-Time Glucose",
                                   .default = "Historic Glucose")),
    type = "line",
    hcaes(x = datetime_to_timestamp(`Date Time`), y = Gl, group = `Condition ID`)) %>%
  # BG data 
   hc_add_series(
    name = "BG Reference",
    data = freestyle %>%
           filter(`Subject ID` == Id),
    type = "scatter",
    color = "#FF0000",
    hcaes(x = datetime_to_timestamp(`BG Date Time`), y = `FreeStyle Reading`)) %>% 
    # Add X label
    hc_xAxis(title = list(text = "Date Time"),
             type = "datetime", 
             dateTimeLabelFormats = list(day = '%d %b %y')) %>%
    # Add Y axis
    hc_yAxis(title = list(text = "Glucose(mg/dl)")) %>%
    # Change the size of marker
    hc_plotOptions(scatter = list(
                            marker = list(radius = 1.9, symbol = "circle"))) %>% 
    # Change the format of point
    hc_tooltip(pointFormat = '{point.x: %Y-%m-%d %H:%M:%S} {point.y:.1f} ')  %>% 
    # Add zoom in function
    hc_chart(zoomType = "xy") %>% 
    # Add navigator
    hc_navigator(enabled = TRUE)
    # {if (UUU %>%
    #      filter(Type != "SENSOR_STARTED (58)") %>%
    #      filter(`Subject ID` == Id) %>% 
    #      nrow() != 0) 
    #      hc_navigator(.,enabled = TRUE) else .}  %>%
    # {if (UUU %>%
    #      filter(Type != "SENSOR_STARTED (58)") %>%
    #      filter(`Subject ID` == Id) %>% 
    #      nrow() == 0) 
    #      hc_navigator(.,enabled = TRUE,series = list(color = "white")) else .} 
}
```

```{r}
# my_plot(Id = "810011", type = "904")
```

```{r eval = params$plot}
#| label: Distinct Subject ID
UD <- UUU %>% 
      distinct(`Subject ID`) %>% 
      pull()
```

```{r eval = params$plot}
#| label: For Loop Plots
plots <- list()
for (i in seq_along(UD)){
  plots[[i]] <- my_plot(Id = UD[i],type = params$type)
}
htmltools::tagList(plots)
```

```{r eval = params$analysis}
#| label: Pair BG function
PAIRBG_fun <- function(data){
  # BG Strips Data
  freestyle %>%
     # Remove Extreme Reference readings <20 or >500
     filter(between(`FreeStyle Reading`,20,500)) %>% 
     full_join(
               # Sensor Data
               data %>%
                mutate(
                  `Lower Bound` = case_when(Type %in% c("904","906") ~ `Date Time` - dminutes(5),
                                            .default = `Date Time` - dminutes(8)),
                  `Upper Bound` = case_when(Type %in% c("904","906") ~ `Date Time` + dminutes(5),
                                            .default = `Date Time` + dminutes(8))
                     ),
                   by = "Subject ID",
                   multiple = "all"
                     ) %>%
      filter(`BG Date Time` >= `Lower Bound`,`BG Date Time` <= `Upper Bound`) %>% 
      # Select the nearest time
      group_by(`Subject ID`,`BG Date Time`) %>%
      arrange(desc(`Date Time`)) %>%
      slice_min(abs(`BG Date Time` - `Date Time`),n = 1,with_ties = F) %>%
      ungroup() %>%
      # Select the nearest time
      group_by(`Subject ID`,`Date Time`) %>%
      arrange(desc(`Date Time`)) %>%
      slice_min(abs(`BG Date Time` - `Date Time`),n = 1,with_ties = F) %>%
      ungroup() %>%
      select(-c(contains("Bound")))
}
```

```{r eval = params$analysis}
#| label: Paired Data
Ap <- UUU %>% 
      # Current Glucose Only
      filter(Type == "904") %>%
      # Remove Extreme Gl readings < 40 or > 400
      filter(between(Gl,40,400)) %>% 
      group_split(`Subject ID`,`Condition ID`,Type) %>%
      # New anonymous function
      map(\(df) PAIRBG_fun(data = df)) %>%
      # formula syntax
      # map(~ PAIRBG_fun(data = .x)) %>%
      list_rbind() %>% 
      # Row-wise Calculation
      mutate(
            # Reference glucose values < 100 mg/dL
            `Difference(mg/dL)` = Gl - `FreeStyle Reading`,
            `Absolute Difference(mg/dL)` = abs(`Difference(mg/dL)`),
            # Reference glucose values >= 100 mg/dL
            `Relative Difference(%)` = (`Difference(mg/dL)`/`FreeStyle Reading`)*100,
            `Absolute Relative Difference(%)` = abs(`Relative Difference(%)`),
            `Hybrid Bias` = case_when(`FreeStyle Reading` < 100 ~ `Difference(mg/dL)`,
                                       .default = `Relative Difference(%)`)
             )
```

```{r}
# Ap105 <- vroom(gsub("\\\\", "/", r"(\\oneabbott.com\dept\ADC\Technical_OPS\Clinical_Affairs\Clinical Study Files\Sensor Systems\ADC-US-RES-16157_InHouse Sensor\Statistics\Programs\SE105\AL\Data\IH105.csv)"),delim = ",",col_names = T,show_col_types = F,col_types = c(`Subject ID` = "c",Type = "c"))
```

```{r eval = params$analysis}
#| label: Import IH105 Paired Data
Ap105 <- open_dataset(gsub("\\\\", "/", r"(\\oneabbott.com\dept\ADC\Technical_OPS\Clinical_Affairs\Clinical Study Files\Sensor Systems\ADC-US-RES-16157_InHouse Sensor\Statistics\Programs\SE105\AL\Data\Ap\part-0.parquet)")) %>%
  collect() 
```

```{r eval = params$analysis}
#| label: Bind Rows and arrange data
Ap <- Ap %>% 
      bind_rows(Ap105) %>% 
      mutate(Data = case_when(str_starts(`Subject ID`,"57") ~ "225 SE07",
                              str_starts(`Subject ID`,"81") ~ "225 SE08",
                              .default =  "IH105"))
```

`r if(params$analysis){knitr::asis_output("# **Difference Measures**")}`
```{r eval = params$analysis}
#| label: difference measure function
diff_measure_fun <- function(..., reference) {
  
diff_calculation <- list(
                          Mean = ~ mean(.x, na.rm = T),
                          Median = ~ median(.x, na.rm = T),
                          SD = ~ sd(.x, na.rm = T),
                          Min = ~ min(.x, na.rm = T),
                          Max = ~ max(.x, na.rm = T),
                          N = ~ sum(!is.na(.x),na.rm = T)
                         )

if (reference == TRUE) {
Ap |> 
   mutate(# Reference Level
          Level = case_when(`FreeStyle Reading` < 100 ~ "<100 mg/dL",
                            .default = ">=100 mg/dL")) |> 
   # Overall Reference Level
   bind_rows(
             Ap |> 
             mutate(Level = "Overall")  
   ) |> 
   pivot_longer(`Difference(mg/dL)`:`Absolute Relative Difference(%)`,names_to = "Measure") |>
   mutate(
          # Factor order Measure
           Measure = fct_inorder(Measure),
          # Lot 
           Lot = str_c("Lot",str_sub(`Condition ID`,3),sep = " ")) |> 
   # Difference(mg/dL) and Absolute Difference(mg/dL) for Reference Level < 100 mg/dL
   # Relative Difference(%) and Absolute Relative Difference(%) for Reference Level >= 100 mg/dL
   filter((Measure %in% c("Difference(mg/dL)", "Absolute Difference(mg/dL)") & 
          Level %in% c("<100 mg/dL", "Overall")) | 
          (Measure %in% c("Relative Difference(%)", "Absolute Relative Difference(%)") & 
          Level %in% c(">=100 mg/dL", "Overall"))) |> 
   # User-Defined group variables
   group_by(...) |> 
   group_by(Measure,.add = TRUE) |> 
   summarise_at(.vars = "value", diff_calculation) |> 
   gt() |>
   cols_align(align = "center") |>
   fmt_number(columns = Mean:Max,decimals = 1)
  } else {
     Ap |> 
   mutate(Lot = str_sub(`Condition ID`,3)) |> 
   group_by(...) |> 
   summarise(
     across(c(`Difference(mg/dL)`:`Absolute Relative Difference(%)`), 
              diff_calculation[1:3],.names = "{.col} {.fn}"), N = n()) |> 
   relocate(N,.after = last_col()) |> 
   gt()  |> 
   cols_align(align = "center") |> 
   tab_spanner(label = "Difference(mg/dL)",columns = c("Difference(mg/dL) Mean","Difference(mg/dL) Median","Difference(mg/dL) SD")) |> 
   tab_spanner(label = "Abs. Difference (mg/dL)",columns = c("Absolute Difference(mg/dL) Mean","Absolute Difference(mg/dL) Median","Absolute Difference(mg/dL) SD")) |> 
   tab_spanner(label = "Relative Difference(%)",columns = c("Relative Difference(%) Mean","Relative Difference(%) Median","Relative Difference(%) SD")) |> 
   tab_spanner(label = "Absolute Relative Difference(%)",columns = c("Absolute Relative Difference(%) Mean","Absolute Relative Difference(%) Median","Absolute Relative Difference(%) SD")) |> 
   fmt_number(columns = contains(c("Mean","Median")),decimals = 1) |> 
   fmt_number(columns = contains(c("SD")),decimals = 2) |> 
    cols_label(
      `Difference(mg/dL) Mean` = "Mean",`Difference(mg/dL) Median` = "Median",
      `Difference(mg/dL) SD` = "SD",
      `Relative Difference(%) Mean` = "Mean",`Relative Difference(%) Median` = "Median",`Relative Difference(%) SD` = "SD",
      `Absolute Difference(mg/dL) Mean` = "Mean",`Absolute Difference(mg/dL) Median` = "Median",
      `Absolute Difference(mg/dL) SD` =  "SD",`Absolute Relative Difference(%) Mean` = "Mean",
      `Absolute Relative Difference(%) Median` = "Median",
      `Absolute Relative Difference(%) SD` = "SD"
    )
   }
}
```

`r if(params$analysis){knitr::asis_output("## Real Time Difference Measures Group by Study Event and Lot")}`
```{r eval = params$analysis}
#| column: page
diff_measure_fun(Data,Lot,Level,reference = T)
```

`r if(params$analysis){knitr::asis_output("## Real Time Difference Measures Group by Lot")}`
```{r eval = params$analysis}
#| column: page
diff_measure_fun(Lot,Level,reference = T)
```

```{r eval = params$analysis}
#| column: page
diff_measure_fun(Data,Lot,reference = F)
```

```{r eval = params$analysis}
#| column: page
# diff_measure_fun(Lot,reference = F)
```

`r if(params$analysis){knitr::asis_output("# **System Agreement Analysis**")}`
```{r eval = params$analysis}
system_agreement_fun <- function(..., long) {
gl_breaks <- c(0,15,20,40,Inf)

if (long == TRUE) {
Ap |> 
   mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
                            .default = ">=70 mg/dL")) |> 
   # Overall 
   bind_rows(Ap |> 
             mutate(Level = "Overall")) |> 
   mutate(Lot = str_c("Lot",str_sub(`Condition ID`,3),sep = " "),
          Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Difference(mg/dL)`,0), breaks = gl_breaks,include.lowest = T),
                            .default = cut(round(`Absolute Relative Difference(%)`,0), breaks = gl_breaks,include.lowest = T))) |> 
   group_by(...) |> 
   count(Level,Group,.drop = F) |> 
   mutate(Sum = sum(n),
          cum = case_when(row_number() %in% c(1:3) ~ cumsum(n),
                .default = n),
          Percent = round((cum/Sum)*100,1)) |> 
   ungroup() |> 
   mutate(Group = rep(c("Within +- 15 mg/dL [0.8 mmol/L]","Within +- 20 mg/dL [1.1 mmol/L]","Within +- 40 mg/dL [2.2 mmol/L]","Outside +- 40 mg/dL [2.2 mmol/L]","Within +- 15%","Within +- 20%","Within +- 40% ","Outside +- 40%"),n()/8),
          `N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) |> 
   group_by(...) |>
   gt() |>
   cols_align(align = "center") |>
   cols_hide(columns = c(n:Percent))
 } else {
   Ap |> 
   mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
                            .default = ">=70 mg/dL")) |> 
   # Overall 
   bind_rows(Ap |> 
             mutate(Level = "Overall")) |> 
   mutate(Lot = str_c("Lot",str_sub(`Condition ID`,3),sep = " "),
          Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Difference(mg/dL)`,0), breaks = gl_breaks,include.lowest = T),
                            .default = cut(round(`Absolute Relative Difference(%)`,0), breaks = gl_breaks,include.lowest = T))) |> 
   group_by(...) |> 
   count(Level,Group,.drop = F) |> 
   mutate(Sum = sum(n),
          cum = case_when(row_number() %in% c(1:3) ~ cumsum(n),
                .default = n),
          Percent = round((cum/Sum)*100,1)) |> 
   ungroup() |> 
   mutate(Group = rep(c("Within +-15% / +-15mg/dL [0.8 mmol/L]","Within +-20% / +-20mg/dL [1.1 mmol/L]","Within +-40% / +-40mg/dL [2.2 mmol/L]","Outside +-40% / +-40mg/dL[2.2 mmol/L]"),n()/4),
          `N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) |> 
   pivot_wider(id_cols = -c(n:Percent),names_from = Group,values_from = `N(%)`) |> 
   group_by(...) |>
   gt() |>
   cols_align(align = "center") |> 
   cols_width(everything() ~ px(200))
 }
}
```

`r if(params$analysis){knitr::asis_output("## Real Time System Accuracy Results Group by Study Event and Lot")}`
```{r eval = params$analysis}
#| column: page
system_agreement_fun(Data,Lot,Level,long = T)
```

`r if(params$analysis){knitr::asis_output("## Real Time System Accuracy Results Group by Study Event and Lot")}`
```{r eval = params$analysis}
#| column: page
system_agreement_fun(Data,Lot,Level,long = F)
```

`r if(params$analysis){knitr::asis_output("## Real Time System Accuracy Results Group by Lot")}`
```{r eval = params$analysis}
#| column: page
system_agreement_fun(Lot,Level,long = F)
```

`r if(params$analysis){knitr::asis_output("## Real Time System Accuracy Plot")}`
```{r eval = params$analysis}
#| column: body-outset
ggplot(Ap) +
  geom_point(aes(x = `FreeStyle Reading`, y = `Difference(mg/dL)`, color = str_sub(`Condition ID`,3), shape = str_sub(`Condition ID`,3))) +
  labs(x = "BG Reference (mg/dL)", y = "Bias (mg/dL)", color = "Lot", shape = "Lot") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),panel.grid.minor.y = element_blank(),legend.position = "bottom",plot.title = element_text(hjust = 0.5))
```

```{r}
# Ap |> 
#    mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
#                             .default = ">=70 mg/dL")) |> 
#    # Overall 
#    bind_rows(Ap |> 
#              mutate(Level = "Overall")) |> 
#    mutate(Lot = str_c("Lot",str_sub(`Condition ID`,3),sep = " "),
#           Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Difference(mg/dL)`,0), breaks = gl_breaks,include.lowest = T),
#                             .default = cut(round(`Absolute Relative Difference(%)`,0), breaks = gl_breaks,include.lowest = T))) |> 
#    group_by(...) |> 
#    count(Level,Group,.drop = F) |> 
#    mutate(Sum = sum(n),
#           cum = case_when(row_number() %in% c(1:3) ~ cumsum(n),
#                 .default = n),
#           Percent = round((cum/Sum)*100,1)) |> 
#    ungroup() |> 
#    mutate(Group = rep(c("Within +-15% / +-15mg/dL [0.8 mmol/L]","Within +-20% / +-20mg/dL [1.1 mmol/L]","Within +-40% / +-40mg/dL [2.2 mmol/L]","Outside +-40% / +-40mg/dL[2.2 mmol/L]"),n()/4),
#           `N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) |> 
#    pivot_wider(id_cols = -c(n:Percent),names_from = Group,values_from = `N(%)`) |> 
#    group_by(...) |>
#    gt() |>
#    cols_align(align = "center") |> 
#    cols_width(everything() ~ px(200))
```

```{r }
# my_table <- function(Condition,type,...){
#   gl_breaks <- c(0,10,15,20,30,40,Inf)
# Ap %>% 
#    # Create User-Defined arguments 
#    filter(Type %in% type, str_sub(`Condition ID`,3) %in% Condition) %>%
#    mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
#                             TRUE ~ ">=70 mg/dL")) %>% 
#    group_by(Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Bias`,0), breaks = gl_breaks,include.lowest = T),
#                               TRUE ~ cut(round(`Absolute Percent Bias`,0), breaks = gl_breaks,include.lowest = T))) %>% 
#    group_by(...) %>% 
#    ungroup() %>%
#    group_split(Level) %>%
#    map(~ count(.x,Group,name = "N",.drop = F)) %>%
#    map(~ mutate(.x,Sum = sum(N),
#                    cum = case_when(row_number() %in% c(1:5) ~ cumsum(N),
#                                    TRUE ~ N),
#                    Percent = round((cum/Sum)*100,1))) %>%
#    # Turn implicit factor levels into explicit
#    map(~ complete(.x,Group)) %>%
#    map_dfr(~ transmute(.x,`N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)"))) %>% 
#    add_column(Group = c("Within +- 10 mg/dL","Within +- 15 mg/dL","Within +- 20 mg/dL","Within +- 30 mg/dL","Within +- 40 mg/dL ","Outside +- 40 mg/dL ","Within +- 10%","Within +- 15%","Within +- 20%","Within +- 30%","Within +- 40% ","Outside +- 40%"),.before = "N(%)") %>% 
#    bind_rows(
#      ## Pooled
#      Ap %>%
#    # Only Real Time
#    filter(Type %in% type, str_sub(`Condition ID`,3) %in% Condition) %>%
#    mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
#                             TRUE ~ ">=70 mg/dL")) %>%
#    group_by(Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Bias`,0), breaks = gl_breaks,include.lowest = T),
#                               TRUE ~ cut(round(`Absolute Percent Bias`,0), breaks = gl_breaks,include.lowest = T))) %>% 
#    ungroup() %>%
#    count(Group,name = "N",.drop = F) %>%
#    mutate(Sum = sum(N),
#           cum = case_when(row_number() %in% c(1:5) ~ cumsum(N),
#                           TRUE ~ N),
#           Percent = round((cum/Sum)*100,1)) %>%
#    transmute(`N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) %>%
#    add_column(Group = c("Within +- 10 mg/dL or 10%","Within +- 15 mg/dL or 15%","Within +- 20 mg/dL or 20%","Within +- 30 mg/dL or 30%","Within +- 40 mg/dL or 40% ","Outside +- 40 mg/dL or 40% "),.before = "N(%)") 
#    ) %>%  
#    gt() %>%
#    cols_align(align = "center") %>%
#    sub_missing(columns = everything(),missing_text = "") %>%
#    tab_row_group(label = "Reference Glucose Overall Levels ",rows = 13:18) %>%
#    tab_row_group(label = "Reference Glucose >= 70 mg/dL ",rows = 7:12) %>%
#    tab_row_group(label = "Reference Glucose < 70 mg/dL",rows = 1:6) %>%
#    opt_table_lines() %>%
#    tab_style(style = list(cell_fill(color = rgb(192,192,192,maxColorValue = 225))),
#              locations = cells_row_groups()) %>%
#    tab_header(title = md("Number and Percent of Results within Reference Glucose")) %>% 
#    as_raw_html()
# }
```


```{r}
#| column: screen
# my_table <- function(type,...) {
# gl_breaks <- c(0,10,15,20,30,40,Inf)
# Ap %>% 
#    # filter(Type %in% type) %>%
#    mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
#                             .default = ">=70 mg/dL"),
#           Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Bias`,0), breaks = gl_breaks,include.lowest = T),
#                             .default = cut(round(`Absolute Percent Bias`,0), breaks = gl_breaks,include.lowest = T)),
#           Lot = str_sub(`Condition ID`,3)) %>% 
#    # group_by(...) %>% 
#    group_by(Data,Level,Lot,Group) %>%
#    summarise(N = n()) %>% 
#    complete(Group,fill = list(N = 0)) %>%
#    mutate(Sum = sum(N),
#           cum = case_when(row_number() %in% c(1:5) ~ cumsum(N),
#                           .default = N),
#                     Percent = round((cum/Sum)*100,1),
#           Group = c("Within +- 10 mg/dL","Within +- 15 mg/dL","Within +- 20 mg/dL","Within +- 30 mg/dL","Within +- 40 mg/dL ","Outside +- 40 mg/dL"),
#           `N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) %>%
#    ungroup() %>%
#    pivot_wider(id_cols = c(Data,Level,Lot),names_from = Group,values_from = `N(%)`) %>% 
#    gt(groupname_col = c("Data","Level")) %>%
#    cols_align(align = "center",columns = everything())
# }
```


```{r}
#| column: screen
# my_table <- function(type,...) {
# gl_breaks <- c(0,10,15,20,30,40,Inf)
# Ap %>% 
#    # filter(Type %in% type) %>%
#    mutate(Level = case_when(`FreeStyle Reading` < 70 ~ "<70 mg/dL",
#                             .default = ">=70 mg/dL"),
#           Group = case_when(`FreeStyle Reading` < 70 ~ cut(round(`Absolute Bias`,0), breaks = gl_breaks,include.lowest = T),
#                             .default = cut(round(`Absolute Percent Bias`,0), breaks = gl_breaks,include.lowest = T)),
#           Lot = str_sub(`Condition ID`,3)) %>% 
#    # group_by(...) %>% 
#    group_by(Level,Lot,Group) %>%
#    summarise(N = n()) %>% 
#    complete(Group,fill = list(N = 0)) %>%
#    mutate(Sum = sum(N),
#           cum = case_when(row_number() %in% c(1:5) ~ cumsum(N),
#                           .default = N),
#                     Percent = round((cum/Sum)*100,1),
#           Group = c("Within +- 10 mg/dL","Within +- 15 mg/dL","Within +- 20 mg/dL","Within +- 30 mg/dL","Within +- 40 mg/dL ","Outside +- 40 mg/dL"),
#           `N(%)` = str_c(cum,"/",Sum," ","(",Percent,"%)")) %>%
#    ungroup() %>%
#    pivot_wider(id_cols = c(Level,Lot),names_from = Group,values_from = `N(%)`) %>% 
#    gt(groupname_col = "Level") %>% 
#    cols_align(align = "center") 
# }
```

```{r}
#| column: screen
# my_table(type = c("904"))
```

```{r}
# tibble(my_table(type = "904",Condition = c("1")),
#        my_table(type = "904",Condition = c("2")),
#        my_table(type = "904",Condition = c("3")),
#        my_table(type = "904",Condition = c("4")),
#        my_table(type = "904",Condition = c("5")),
#        my_table(type = "904",Condition = c("6"))
#        ) %>% 
#     gt() %>% 
#     fmt_markdown(columns = everything()) %>% 
#     cols_label(`my_table(type = "904", Condition = c("1"))` = "Lot = 1",
#                `my_table(type = "904", Condition = c("2"))` = "Lot = 2",
#                `my_table(type = "904", Condition = c("3"))` = "Lot = 3",
#                `my_table(type = "904", Condition = c("4"))` = "Lot = 4",
#                `my_table(type = "904", Condition = c("5"))` = "Lot = 5",
#                `my_table(type = "904", Condition = c("6"))` = "Lot = 6")
```
